Astr 513: Final Project

### 2016-04-28 Final_Project/ms.tex
Added todo notes commands for each of us to write messages.
Added an example figure and added new sections.

\usepackage{todonotes}
\newcommand\TM[1]{\todo[color=green!40, inline, size=\small]{TM: #1}}

@@

>>>>

\usepackage{todonotes}
\newcommand\TM[1]{\todo[color=green!40, inline, size=\small]{TM: #1}}
\newcommand\EW[1]{\todo[color=blue!40, inline, size=\small]{TM: #1}}
\newcommand\LC[1]{\todo[color=magenta!40, inline, size=\small]{TM: #1}}

@@

\subsection{Covariances}
\label{sec:covariances}
\TM{A subsection that explains how the covariance matrix looks. Basically
  a brief discussion about how it was made and then a picture of the 
  {\it correlation} matrix. Example figure below.}

\begin{figure}
 \includegraphics[width=\linewidth]{figures/clusters-randoms_noqc_correlation_subset.eps}
 \caption{Correlation matrix example. We will just have one panel.}
 \label{fig:cmatrix}
\end{figure}

\section{$\mu$ Model}
\label{sec:model}
\TM{This explains how to go from a cosmology to $\mu(z)$.}

\subsection{Likelihood}
\label{sec:likelihood}
\TM{This has our likelihood.}
